### 2015-03-09 Projects/DelCo_2012/Report/DelCo_2012.tex
Updated gas cooling descriptions.

The Engineering Laboratory at National Institute of Standards and Technology has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.  One of the objectives of this program is to examine non-traditional means of fire suppression.   This series of experiments conducted by NIST for the California Polytechnic State University, San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.  These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.  
NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for different compartment fire scenarios.

@@

1)            spray density measures under non-fire conditions 
2)            gas layer cooling 
3)            fire suppression in an experimental structures

@@

@@

\subsection{Burn Building - Gas Cooling}
\label{sec:Burn_Building}

@@

>>>>

The Engineering Laboratory at National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.  One of the objectives of this program is to examine non-traditional means of fire suppression.   This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.  These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.

NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for different compartment fire scenarios.

@@

1)            spray density measures under non-fire conditions 
2)            gas layer cooling 
3)            fire suppression in an experimental structure

@@

The purpose built fire training structure was used for a total of eighty eight experiments studying the effectiveness of cooling the upper gas layer in an adjacent space to the area of fire involvement. These tests examined five different hose stream patterns through two nozzle types for both compressed air foam and typical water suppression. The area of the purpose built structure used for these experiments was located on the ground floor and involved two adjoining rooms.  The fire was ignited and allowed to grow and fill the compartment with heated fire products and flame.  The developing hot gas layer spread to the adjacent room through a single doorway.  The adjacent room developed a hot gas layer and was the focus of this series of tests.

@@

\subsection{Purpose Built Fire Training Structure - Gas Cooling}
\label{sec:Burn_Building}

@@

Wood pallets were used to provide the fuel for the fire used in the gas cooling experiments.  The pallets were approximately   1.2 m (4.0 ft) by 1.0 m (3.3 ft) by 0.13 m (0.42 ft) thick.  Forty eight of the pallets used to fuel the gas cooling experiments were weighed.  The pallets ranged in mass from 13.6 kg (29.9 lbs) to 26.4 kg (58.1 lbs) with an average of 18.4 kg (40.5 lbs).  The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig xx.  Approximately one half of a bale of excelsior, 13.0  kg (28.6 lbs), was mixed with the pallets to aid with ignition.

As the pallets burned burn away and the hot gas layer temperatures decreased, the steel shutters on the window to the fire room were opened and additional pallets were added to the piles of burning pallets until the flames from the piles reached the ceiling of the burn room again.  The number of pallets added each time varied.
